Estimating survival in left filtered data

### 2022-03-04 reports/resources/sensitivity/results_2.tex
SER

% Created by tikzDevice version 0.12.3.1 on 2022-01-19 23:23:08
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 79.54) --
	(306.77, 79.54);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,105.93) --
	(306.77,105.93);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,132.32) --
	(306.77,132.32);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 66.34) --
	(306.77, 66.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 92.73) --
	(306.77, 92.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,119.12) --
	(306.77,119.12);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.70,145.51) --
	( 60.69,145.51) --
	( 73.67,145.51) --
	( 86.66,143.30) --
	( 99.65,140.75) --
	(112.63,138.01) --
	(125.62,134.78) --
	(138.60,131.40) --
	(151.59,128.22) --
	(164.57,124.71) --
	(177.56,121.64) --
	(190.55,118.40) --
	(203.53,115.01) --
	(216.52,111.80) --
	(229.50,109.04) --
	(242.49,106.38) --
	(255.47,103.32) --
	(268.46, 99.77) --
	(281.44, 96.75) --
	(294.43, 85.15);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.70,145.51) --
	( 60.69,145.51) --
	( 73.67,145.51) --
	( 86.66,142.38) --
	( 99.65,138.02) --
	(112.63,133.41) --
	(125.62,128.63) --
	(138.60,124.26) --
	(151.59,119.71) --
	(164.57,115.31) --
	(177.56,111.16) --
	(190.55,106.98) --
	(203.53,103.08) --
	(216.52, 99.10) --
	(229.50, 95.50) --
	(242.49, 91.83) --
	(255.47, 88.16) --
	(268.46, 84.67) --
	(281.44, 81.50) --
	(294.43, 68.52);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,144.58) --
	( 73.67,143.55) --
	( 86.66,142.41) --
	( 99.65,141.16) --
	(112.63,139.78) --
	(125.62,138.35) --
	(138.60,136.78) --
	(151.59,135.15) --
	(164.57,133.48) --
	(177.56,131.78) --
	(190.55,130.01) --
	(203.53,128.23) --
	(216.52,126.40) --
	(229.50,124.54) --
	(242.49,122.68) --
	(255.47,120.85) --
	(268.46,118.98) --
	(281.44,117.13) --
	(294.43,115.03);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,144.30) --
	( 73.67,142.98) --
	( 86.66,141.51) --
	( 99.65,139.92) --
	(112.63,138.20) --
	(125.62,136.41) --
	(138.60,134.48) --
	(151.59,132.46) --
	(164.57,130.39) --
	(177.56,128.31) --
	(190.55,126.17) --
	(203.53,123.97) --
	(216.52,121.74) --
	(229.50,119.50) --
	(242.49,117.29) --
	(255.47,115.06) --
	(268.46,112.77) --
	(281.44,110.57) --
	(294.43,108.03);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,142.77) --
	( 73.67,139.94) --
	( 86.66,136.99) --
	( 99.65,133.96) --
	(112.63,130.76) --
	(125.62,127.69) --
	(138.60,124.46) --
	(151.59,121.22) --
	(164.57,118.02) --
	(177.56,114.80) --
	(190.55,111.53) --
	(203.53,108.40) --
	(216.52,105.20) --
	(229.50,102.00) --
	(242.49, 98.82) --
	(255.47, 95.78) --
	(268.46, 92.70) --
	(281.44, 90.00) --
	(294.43, 87.25);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,141.95) --
	( 73.67,138.32) --
	( 86.66,134.53) --
	( 99.65,130.68) --
	(112.63,126.70) --
	(125.62,122.87) --
	(138.60,118.92) --
	(151.59,114.92) --
	(164.57,110.94) --
	(177.56,107.05) --
	(190.55,103.11) --
	(203.53, 99.27) --
	(216.52, 95.40) --
	(229.50, 91.58) --
	(242.49, 87.82) --
	(255.47, 84.15) --
	(268.46, 80.43) --
	(281.44, 77.26) --
	(294.43, 73.99);
\definecolor{drawColor}{gray}{0.20}

@@

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,107.02) {Scenario 1};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{gray}{0.20}

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 63.59) {0.85};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 89.98) {0.90};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,116.37) {0.95};

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 66.34) --
	( 35.37, 66.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 92.73) --
	( 35.37, 92.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,119.12) --
	( 35.37,119.12);

>>>>

% Created by tikzDevice version 0.12.3.1 on 2022-01-19 23:23:09
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 79.59) --
	(306.77, 79.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,105.96) --
	(306.77,105.96);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,132.33) --
	(306.77,132.33);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 66.41) --
	(306.77, 66.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 92.78) --
	(306.77, 92.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,119.15) --
	(306.77,119.15);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.70,145.51) --
	( 60.69,145.51) --
	( 73.67,145.51) --
	( 86.66,143.56) --
	( 99.65,140.66) --
	(112.63,137.87) --
	(125.62,134.78) --
	(138.60,131.62) --
	(151.59,128.18) --
	(164.57,124.69) --
	(177.56,121.35) --
	(190.55,118.00) --
	(203.53,114.85) --
	(216.52,111.79) --
	(229.50,108.62) --
	(242.49,105.56) --
	(255.47,102.37) --
	(268.46, 99.47) --
	(281.44, 96.31) --
	(294.43, 83.75);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.70,145.51) --
	( 60.69,145.51) --
	( 73.67,145.51) --
	( 86.66,142.18) --
	( 99.65,138.42) --
	(112.63,133.91) --
	(125.62,129.39) --
	(138.60,124.77) --
	(151.59,120.43) --
	(164.57,116.37) --
	(177.56,112.09) --
	(190.55,107.64) --
	(203.53,103.68) --
	(216.52, 99.99) --
	(229.50, 96.45) --
	(242.49, 92.45) --
	(255.47, 88.73) --
	(268.46, 85.08) --
	(281.44, 81.53) --
	(294.43, 68.52);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,144.57) --
	( 73.67,143.54) --
	( 86.66,142.38) --
	( 99.65,141.07) --
	(112.63,139.64) --
	(125.62,138.17) --
	(138.60,136.55) --
	(151.59,134.92) --
	(164.57,133.20) --
	(177.56,131.42) --
	(190.55,129.59) --
	(203.53,127.78) --
	(216.52,125.83) --
	(229.50,123.91) --
	(242.49,121.96) --
	(255.47,120.00) --
	(268.46,118.06) --
	(281.44,116.12) --
	(294.43,114.08);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,144.29) --
	( 73.67,142.96) --
	( 86.66,141.49) --
	( 99.65,139.85) --
	(112.63,138.10) --
	(125.62,136.23) --
	(138.60,134.24) --
	(151.59,132.15) --
	(164.57,129.99) --
	(177.56,127.79) --
	(190.55,125.59) --
	(203.53,123.36) --
	(216.52,121.03) --
	(229.50,118.72) --
	(242.49,116.41) --
	(255.47,114.18) --
	(268.46,111.87) --
	(281.44,109.56) --
	(294.43,106.98);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,142.74) --
	( 73.67,139.90) --
	( 86.66,136.92) --
	( 99.65,133.75) --
	(112.63,130.48) --
	(125.62,127.33) --
	(138.60,124.04) --
	(151.59,120.82) --
	(164.57,117.55) --
	(177.56,114.24) --
	(190.55,110.90) --
	(203.53,107.74) --
	(216.52,104.39) --
	(229.50,101.12) --
	(242.49, 97.80) --
	(255.47, 94.60) --
	(268.46, 91.44) --
	(281.44, 88.64) --
	(294.43, 85.98);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,141.92) --
	( 73.67,138.26) --
	( 86.66,134.46) --
	( 99.65,130.50) --
	(112.63,126.48) --
	(125.62,122.52) --
	(138.60,118.48) --
	(151.59,114.40) --
	(164.57,110.31) --
	(177.56,106.24) --
	(190.55,102.24) --
	(203.53, 98.39) --
	(216.52, 94.42) --
	(229.50, 90.53) --
	(242.49, 86.65) --
	(255.47, 83.04) --
	(268.46, 79.32) --
	(281.44, 76.03) --
	(294.43, 72.72);
\definecolor{drawColor}{gray}{0.20}

@@

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,107.02) {Scenario 2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{gray}{0.20}

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 63.65) {0.85};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 90.02) {0.90};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,116.39) {0.95};

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 66.41) --
	( 35.37, 66.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 92.78) --
	( 35.37, 92.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,119.15) --
	( 35.37,119.15);

### 2022-03-04 reports/resources/sensitivity/results_3.tex
SER

% Created by tikzDevice version 0.12.3.1 on 2022-01-19 23:23:09
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 79.59) --
	(306.77, 79.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,105.96) --
	(306.77,105.96);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,132.33) --
	(306.77,132.33);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 66.41) --
	(306.77, 66.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 92.78) --
	(306.77, 92.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,119.15) --
	(306.77,119.15);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.70,145.51) --
	( 60.69,145.51) --
	( 73.67,145.51) --
	( 86.66,143.56) --
	( 99.65,140.66) --
	(112.63,137.87) --
	(125.62,134.78) --
	(138.60,131.62) --
	(151.59,128.18) --
	(164.57,124.69) --
	(177.56,121.35) --
	(190.55,118.00) --
	(203.53,114.85) --
	(216.52,111.79) --
	(229.50,108.62) --
	(242.49,105.56) --
	(255.47,102.37) --
	(268.46, 99.47) --
	(281.44, 96.31) --
	(294.43, 83.75);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.70,145.51) --
	( 60.69,145.51) --
	( 73.67,145.51) --
	( 86.66,142.18) --
	( 99.65,138.42) --
	(112.63,133.91) --
	(125.62,129.39) --
	(138.60,124.77) --
	(151.59,120.43) --
	(164.57,116.37) --
	(177.56,112.09) --
	(190.55,107.64) --
	(203.53,103.68) --
	(216.52, 99.99) --
	(229.50, 96.45) --
	(242.49, 92.45) --
	(255.47, 88.73) --
	(268.46, 85.08) --
	(281.44, 81.53) --
	(294.43, 68.52);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,144.57) --
	( 73.67,143.54) --
	( 86.66,142.38) --
	( 99.65,141.07) --
	(112.63,139.64) --
	(125.62,138.17) --
	(138.60,136.55) --
	(151.59,134.92) --
	(164.57,133.20) --
	(177.56,131.42) --
	(190.55,129.59) --
	(203.53,127.78) --
	(216.52,125.83) --
	(229.50,123.91) --
	(242.49,121.96) --
	(255.47,120.00) --
	(268.46,118.06) --
	(281.44,116.12) --
	(294.43,114.08);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,144.29) --
	( 73.67,142.96) --
	( 86.66,141.49) --
	( 99.65,139.85) --
	(112.63,138.10) --
	(125.62,136.23) --
	(138.60,134.24) --
	(151.59,132.15) --
	(164.57,129.99) --
	(177.56,127.79) --
	(190.55,125.59) --
	(203.53,123.36) --
	(216.52,121.03) --
	(229.50,118.72) --
	(242.49,116.41) --
	(255.47,114.18) --
	(268.46,111.87) --
	(281.44,109.56) --
	(294.43,106.98);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,142.74) --
	( 73.67,139.90) --
	( 86.66,136.92) --
	( 99.65,133.75) --
	(112.63,130.48) --
	(125.62,127.33) --
	(138.60,124.04) --
	(151.59,120.82) --
	(164.57,117.55) --
	(177.56,114.24) --
	(190.55,110.90) --
	(203.53,107.74) --
	(216.52,104.39) --
	(229.50,101.12) --
	(242.49, 97.80) --
	(255.47, 94.60) --
	(268.46, 91.44) --
	(281.44, 88.64) --
	(294.43, 85.98);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,141.92) --
	( 73.67,138.26) --
	( 86.66,134.46) --
	( 99.65,130.50) --
	(112.63,126.48) --
	(125.62,122.52) --
	(138.60,118.48) --
	(151.59,114.40) --
	(164.57,110.31) --
	(177.56,106.24) --
	(190.55,102.24) --
	(203.53, 98.39) --
	(216.52, 94.42) --
	(229.50, 90.53) --
	(242.49, 86.65) --
	(255.47, 83.04) --
	(268.46, 79.32) --
	(281.44, 76.03) --
	(294.43, 72.72);
\definecolor{drawColor}{gray}{0.20}

@@

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,107.02) {Scenario 2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{gray}{0.20}

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 63.65) {0.85};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 90.02) {0.90};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,116.39) {0.95};

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 66.41) --
	( 35.37, 66.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 92.78) --
	( 35.37, 92.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,119.15) --
	( 35.37,119.15);

>>>>

% Created by tikzDevice version 0.12.3.1 on 2022-01-19 23:23:10
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 81.03) --
	(306.77, 81.03);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,106.82) --
	(306.77,106.82);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,132.62) --
	(306.77,132.62);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 68.14) --
	(306.77, 68.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 93.93) --
	(306.77, 93.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,119.72) --
	(306.77,119.72);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.70,145.51) --
	( 60.69,145.51) --
	( 73.67,145.51) --
	( 86.66,143.21) --
	( 99.65,140.90) --
	(112.63,138.18) --
	(125.62,135.32) --
	(138.60,132.01) --
	(151.59,128.88) --
	(164.57,125.81) --
	(177.56,122.56) --
	(190.55,119.26) --
	(203.53,116.07) --
	(216.52,112.97) --
	(229.50,110.06) --
	(242.49,107.05) --
	(255.47,104.22) --
	(268.46,101.10) --
	(281.44, 98.28) --
	(294.43, 86.66);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.70,145.51) --
	( 60.69,145.51) --
	( 73.67,145.51) --
	( 86.66,142.29) --
	( 99.65,138.13) --
	(112.63,133.67) --
	(125.62,129.44) --
	(138.60,125.11) --
	(151.59,120.93) --
	(164.57,116.41) --
	(177.56,112.32) --
	(190.55,108.15) --
	(203.53,104.42) --
	(216.52,100.52) --
	(229.50, 96.63) --
	(242.49, 92.83) --
	(255.47, 89.22) --
	(268.46, 85.32) --
	(281.44, 81.88) --
	(294.43, 68.52);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,144.63) --
	( 73.67,143.62) --
	( 86.66,142.51) --
	( 99.65,141.29) --
	(112.63,139.95) --
	(125.62,138.54) --
	(138.60,137.02) --
	(151.59,135.44) --
	(164.57,133.82) --
	(177.56,132.12) --
	(190.55,130.42) --
	(203.53,128.69) --
	(216.52,126.93) --
	(229.50,125.14) --
	(242.49,123.36) --
	(255.47,121.55) --
	(268.46,119.66) --
	(281.44,117.85) --
	(294.43,115.82);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,144.30) --
	( 73.67,142.91) --
	( 86.66,141.47) --
	( 99.65,139.90) --
	(112.63,138.18) --
	(125.62,136.39) --
	(138.60,134.49) --
	(151.59,132.46) --
	(164.57,130.47) --
	(177.56,128.40) --
	(190.55,126.28) --
	(203.53,124.07) --
	(216.52,121.82) --
	(229.50,119.52) --
	(242.49,117.32) --
	(255.47,115.08) --
	(268.46,112.76) --
	(281.44,110.61) --
	(294.43,108.08);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,142.91) --
	( 73.67,140.14) --
	( 86.66,137.29) --
	( 99.65,134.33) --
	(112.63,131.21) --
	(125.62,128.19) --
	(138.60,125.06) --
	(151.59,121.93) --
	(164.57,118.81) --
	(177.56,115.61) --
	(190.55,112.47) --
	(203.53,109.42) --
	(216.52,106.36) --
	(229.50,103.27) --
	(242.49,100.21) --
	(255.47, 97.22) --
	(268.46, 94.11) --
	(281.44, 91.46) --
	(294.43, 88.80);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,141.95) --
	( 73.67,138.09) --
	( 86.66,134.39) --
	( 99.65,130.57) --
	(112.63,126.61) --
	(125.62,122.77) --
	(138.60,118.86) --
	(151.59,114.84) --
	(164.57,111.04) --
	(177.56,107.14) --
	(190.55,103.26) --
	(203.53, 99.39) --
	(216.52, 95.50) --
	(229.50, 91.58) --
	(242.49, 87.85) --
	(255.47, 84.17) --
	(268.46, 80.40) --
	(281.44, 77.31) --
	(294.43, 74.04);
\definecolor{drawColor}{gray}{0.20}

@@

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,107.02) {Scenario 3};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{gray}{0.20}

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 65.38) {0.85};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 91.17) {0.90};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,116.97) {0.95};

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 68.14) --
	( 35.37, 68.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 93.93) --
	( 35.37, 93.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,119.72) --
	( 35.37,119.72);
